%   Filename    : acknowledgment.tex 
\begin{center}
	\textbf{Acknowledgment}
\end{center}

We would like to express our gratitude to everyone who has contributed their time, knowledge, and support toward the successful completion of this special problem. This journey would not have been possible without the help of many individuals who have motivated and inspired us along the way.

First and foremost, we are deeply grateful to our thesis adviser, Sir Francis Dimzon, for his invaluable guidance, patience, and insightful feedback, which have been significant throughout this project. His expert advice and support pushed us to explore unfamiliar technologies and tackle challenging tasks we had never attempted before. These experiences significantly broadened our skills and perspective, ultimately helping us grow both academically and personally.

We also extend our gratitude to Ma’am Susci Ann Sobrevega and the staff of the Research Resource Center (RRC) for their generous assistance, expertise, and encouragement. Their practical insights and technical support greatly contributed to the development and refinement of the system presented in this work.

Once again, we are sincerely thankful to all who contributed to the success of this special problem. Your support, in both big and small ways, has made a lasting impact on our journey. This work would not have been possible without your encouragement, guidance, and belief in our potential.

\vspace{0.5em}
\hfill \textbf{TUKIB Development Team}

%In addition to the individuals and institutions mentioned above, we would also like to take this opportunity to express our personal gratitude. Each of us has been shaped and supported by different people throughout this journey, and the following messages reflect our individual journeys and heartfelt appreciation.


%[edit hehe]
%I am also sincerely thankful to my special problem groupmates, Nang Sheryl and Kzlyr, for their dedication, collaboration, and hard work—not just during this project, but ever since our internship began. Your willingness to help one another, share responsibilities, and stay committed to our goals made this journey both manageable and meaningful.

%To my family, words cannot express my deepest appreciation for their unconditional love, understanding, and encouragement. Their constant faith in my abilities provided me with the strength and motivation to persevere, especially during difficult times. Their sacrifices and support have been the foundation of my academic journey.

%I would also like to thank my friends—Kurt, John Luis, Chester, John Hamir, Jeff, Josaiah, Nong Jose, and the GD girls—who have been a source of joy, motivation, and encouragement. Their friendship, advice, and moments of laughter helped me maintain balance and stay positive throughout the demanding phases of this project.

%To my special someone, Szophia, thank you for being my rock. Your unwavering support, comfort, and companionship have been invaluable. You have kept me grounded, encouraged me during moments of doubt, and even provided sustenance when I needed it most. You have truly been my study buddy and my greatest supporter.

%Lastly, I am profoundly grateful to God for granting me good health, strength, and resilience throughout this journey. For the times when I felt overwhelmed, I found solace in prayer and faith, which helped me overcome challenges and remain hopeful.

%\vspace{0.5em}
%\hfill \textbf{Rainer Mayagma}